---
title: "W_UP_01"
author: "Cleo Ware"
date: "fall 2023"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file = "pushups.csv", fileEncoding = "UTF-8")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of pushups of line vs skill players

$H_A$: The average number of pushups done by line players is statistically different than that of skill players.

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->
### Plot boxplots

## Now add in boxplot

```{r include=TRUE,echo=FALSE}
ggplot(mydata, aes(x = position, y = pushups)) +
  geom_boxplot() +
  labs(title = "Pushup Positions Comparison",
       x = "Position",
       y = "Number of Pushups") +
  theme(plot.title = element_text(hjust = 0.5, size = 16))
```


When looking at the chart above, it shows that the skill players (on the right)   25% percentile is doing a lot more pushups then the line players (on the left) 75%   percentile.  

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(pushups~position,data=mydata)
```
Mean of skills is higher than the mean of line.

## Inferential Results

<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
```{r}
t.test(pushups~position,data=mydata)
```

p-value = 0.000009421

The p-value is far smaller than 0.05 indicated that there is a strong statistical significance.

This rejects the $H_0$ leaving only the $H_A$.

# Discussion and Conclusion

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variables causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

$H_0$ = There is no difference in push-ups based on position.
$H_A$ = There is a difference in push-ups based on position.

With assistance from ChatGPT I was able to write some R code to create a box plot

Also, by using the Numerical-Cat tool I was able to proform a T Test and summary of the data (favstats). 

The box plot in conjunction with the summary and Test show that we can reject the $H_0$ leaving only the $H_A$. 

$H_0$